---
title: "Unit 1 - 3 Review Starter"
author: "code is lyfe"
date: "2/23/23"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sites <- read_csv("data/sand_minerals.csv")
location_descriptions <- read_csv("data/location_descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility_hardness.csv")
```

## Exercises

### Exercise 1

```{r inspect-sand-minerals}
glimpse(sites)

```
There are 23 rows of data and 2 columns 

Each row is a location corresponding with the mineral found at the location. location = col_double()
minerals = col_characters()

```{r}
glimpse(sites) %>%
 names()
```


### Exercise 2

```{r inspect-other-dataframes}
glimpse(density)
glimpse(solubility_hardness)
glimpse(location_descriptions)

```
```{r}
glimpse(density) %>% 
  names()
glimpse(solubility_hardness) %>% 
  names()
glimpse(location_descriptions) %>%
  names()

```

In density data frame there three rows and 2 columns. Density shows the weight of the mineral itself. In the solubility hardness has 3 rows and columns. Hardness is based of the hardness scale. It shows what possible force can leave a mark on the mineral. The location description has 10 rows and 2 columns. Location tells you where exactly the mineral can be found. For example, one mineral can be found by water or far from.


### Exercise 3

```{r join_mineral_properties}

density%>%
left_join(sites)

```

There are 23 rows in this output which is the same as the amount of rows in the sand minerals dataset. 

```{r}
sand_mineral_density <- density%>%
left_join(sites)
```

```{r}
sand_mineral_density %>%
  left_join(solubility_hardness)

```

```{r}
sand_mineral_properties <- sand_mineral_density %>%
  left_join(solubility_hardness)
```

### Exercise 4
```{r}
sand_mineral_properties %>% 
  count(location)
```
```{r}
sand_mineral_properties %>% 
  slice(1:10)
```
```{r}
sand_mineral_properties %>% 
  slice(1:13) %>% 
  arrange(desc(density))

```
```{r}
sand_mineral_properties %>% 
slice(1:18) 

```
```{r}
sand_mineral_properties %>% 
  filter(na.rm=TRUE) %>% 
  arrange(desc(density))%>%
  slice(6:23)

```


### Exercise 5

Remove this text, and add your answer for Exercise 5 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

## Part II - Data Visualization

`starwars` is already loaded within the `dplyr` package (within `tidyverse`)

### Exercise 7

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 8

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 9

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.
